Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Tweak wording
And note for @eco-ben !

![Partial Dependence Plot indicating the estimated probability (via Random Forest
classification) of cluster assignment along interacting values of median reef depth (meters)
and log10-weighted incoming connectivity. Colour (ranging from dark purple to yellow)
indicates the probability of assignment to each cluster, with brighter colour indicating
higher probability of assignment. Panels A, B, and C illustrates the assignment probability
for Low, Medium, and High cover clusters respectively. The distribution of reef depth and
incoming connectivity values are shown in Panels D and
E.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
fig-align="center" width="14.82cm"}

Individual feature analysis for carrying capacity indicates that its influence on cluster
assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp). This
aligns with the right-skewed distribution of carrying capacity across reefs for these three
predictor variables. Beyond this low-end range, the partial dependence becomes near
constant, indicating that outlier values for these factors are not influential.

Assessing random forest prediction accuracy across bioregions, reveals increasing
performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf). This
highlights that unexplained variation in the test dataset (33% of variation) may be
concentrated in shallow bioregions where the available model predictors do not capture
differences between clustered reefs.

@@

![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
(y-axis) and reef median depth (left panel) and reef log10 weighted incoming connectivity
values (right panel). Point colour represents the threshold assessment values used to assess
positive carbonate budget status ($\theta_0$). Deeper reefs are better able to maintain
cover above the indicative carbonate budget threshold, while there is no considerable
relationship between weighted incoming connectivity and carbonate budget maintenance.
Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}

>>>>

![Partial Dependence Plot indicating the estimated probability (via Random Forest
classification) of cluster assignment along interacting values of median reef depth (meters)
and log10-weighted incoming connectivity. Colour (ranging from dark purple to yellow)
indicates the probability of assignment to each cluster, with brighter shades indicating
higher probability of assignment. Panels A, B, and C illustrates the assignment probability
for Low, Medium, and High cover clusters respectively. The distribution of reef depth and
incoming connectivity values are shown in Panels D and
E.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
fig-align="center" width="14.82cm"}

Individual feature analysis for carrying capacity indicates that its influence on cluster
assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp). This
aligns with the right-skewed distribution of carrying capacity across reefs for these three
predictor variables. Beyond this low-end range, the partial dependence becomes near
constant, indicating that outlier values for these factors are not influential. Assessing
random forest prediction accuracy across bioregions, reveals increasing performance as
bioregion mean reef depth increases (@sfig-rf-predictor-perf). This highlights that
unexplained variation in the test dataset (33% of variation) may be concentrated in shallow
bioregions where the available model predictors do not capture differences between clustered
reefs.

@@

![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
shows relationship between reef median depth, while the right panel shows the same for
log10-weighted incoming connectivity values. Point colour (purple to yellow) represents
($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have
increased number of years above the considered range of $\theta_0$, while no relationship
between weighted incoming connectivity and carbonate budget maintenance was found. **\[Ben,
no x-axis label for Right
Panel?\]**](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}
